\papertitle

### 2012-10-12 manuscript.tex
Added LaTeX fonts to the drawings.
added heat map

Many of the control laws that previous researches have developed from the 
dynamic models of flapping-winged flight are computationally complex and 
require powerful on-board computing [CITATIONS]. In our work, we develop a 
simpler, less computationally intensive method of control for negotiating 
narrow passages.

@@

The high pitch angles H$^2$Bird achieves in routine flight distinguishes it 
from other MAVs. Baek~\cite{baek:tracking} 
demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal using both analytical and empirical methods. We conducted 
experiments to validate this model.

@@

\subsubsection{Reachability Model}
\label{sec:visual_servoing}
%TODO make these span the page, with identical scales/style
\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and perimeter experimental trials overlayed.}
\label{fig:flight_paths}
\end{minipage}
\end{figure*}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{figure}

>>>>

Many of the control laws that previous researches have developed from the 
dynamic models of flapping-winged flight are computationally complex and 
require powerful on-board computing [CITATIONS]. In our work, we develop a 
simpler, less computationally intensive method of control for negotiating 
narrow passages similar to the method presented in [Velocity and Altitude Control of An Ornithopter Micro Aerial Vehicle].

@@

The high pitch angles H$^2$Bird achieves in routine flight distinguishes it 
from other MAVs. Baek 
demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation~\cite{baek:tracking}. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal using both analytical and empirical methods. We conducted 
experiments to validate this model.

@@

\subsubsection{Reachability Model}
\label{sec:visual_servoing}
%TODO make these span the page, with identical scales/style

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{CAPTION.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and perimeter experimental trials overlayed.}
\label{fig:flight_paths}
\end{minipage}
\end{figure*}
